The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
reflow
reflow and newpage for refs
fst draft habitat perspective

## Habitat selection and space use

* Mayor et al. 2009 paper 
* MRSF Laforge paper 
* van Beest et al. 2014 scale paper 
* 1st/2nd/3rd order selection
* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
* Multi-scale habitat selection modeling: a review and outlook

>>>>

## Habitat selection and space use
### 1
Habitat selection and shared space use *link to social*
Habitat selection depends on 
species specific
individual differences in home range and habitat selection
percentage of home range overlap links to foraging quality and availability in herbivores
multilayer networks are "a potential framework" for investigating social dynamics given shared space use and individual habitat selection

### 2
Sociality / multilayer have been used with habitat selection and space use
... examples

Fortin 2009 showed that "bison selection of habitat and landscape features was mediated
by social group size, hypothesizing the predation risk avoidance is the strongest driver of habitat selection"

Banks 2007 habitat fragmentation influences + increased mate availability given increased home range overlap when resource availability was higher

mcloughlin2000 variable response bears to habitat quality and space use/home range overlap

### 3
Scale + habitat selection and space use
types of scale to consider in these types of ML nets

McGarigal 2016 organisms select habitat at multiple scales, temporal spatial 
should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics

Johnson 1980 1st order = selection of the physical or geographical range of a species
2nd order = selection of a home range of an individual or social group
3rd order = selection of various habitat patches within the home range 
4th order = selection of specific resources within a habitat patch

* Mayor et al. 2009 paper 
* MRSF Laforge paper 
* van Beest et al. 2014 scale paper 
* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
* Multi-scale habitat selection modeling: a review and outlook

### 4
how to combine moving forward
multilayer networks across landcover types
in areas of high selection/low selection or favorable/unfavorable habitat
combined with seasonality

in our case study, we looked at increase spatial scales of landcover metrics

we could define layers of the multilayer network according to home range overlap 
instead of specific associations
looking at broader temporal scales and coarser spatial resolutions
